Report On:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe

### 2021-03-13 Phys 311/CTA/Paper/paper.tex
Add Figures

@@

\title{CTA Proposal:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe}

@@

The low metallicity of early stars, specifically stars with high [$\alpha$/Fe] and low [Fe/H] values, indicate that their
nucleosynthesis occurred during a period after the first round of core-collapse supernovae but before large numbers of
Type Ia supernovae events. For decades scientists looked early stars in the halo of the Milky Way to study the early universe.
These Milky Way halo stars have [Fe/H] values of $< -1.0$.

In the past decade efforts such as the Sloan Digital Sky Survey (SDSS) have uncovered a plethora of very dim dwarf spheroidal
(dSph) galaxies and ultra faint dwarfs. These dSph and ultra faint dwarfs have total luminosities in the range of
\(10^{5} L_{\odot} \lesssim L \lesssim 10^{7} L_{\odot}\) and \(L \lesssim 10^5 L_{\odot}\), respectively, which contain
stars with [Fe/H] values of $\sim -2.5$. With the use of medium resolution spectroscopy scientists recently uncovered a
moderate population of super low metal stars with [Fe/H] values $< -3.0$ within ultra fain dwarfs. Within the same systems
scientists did not find any stars with [Fe/H] $> -1.0$. In this population one galaxy, SEGUE-1, stood out from the rest. 
SEGUE-1's population of stars show increasing metallicity, in the form of $\alpha$-elements, but do not exhibit decreasing
[$\alpha$/Fe] ratios. 
This would indicate that the star formation phase in SEGUE-1 occurred before most, if not all, Type Ia supernovae events. This
also indicates that there was likely only one star formation phase within the galaxy.

\section{Novelty and Methods} \label{sec:novelty}

The authors of this paper made new spectrography measurements of six stars within SEGUE-1 using the Magellan/MIKE and Keck/HIRES
spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
stars that were chosen were the brightest stars in SEGUE-1 which allowed for high resolution spectrography. Using the spectrographs
the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, and neutron-capture elements.
The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
The parameters for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
noise ratio (S/N) was only moderate with values between 20 and 50

\section{Results, Discussion, and Future Work} \label{sec:dicussion}

@@

%% Figure of spectra

@@

%% Fig of [X/Fe] vs [Fe/H]

@@

%% Fig of Enrichment Behavior

@@

>>>>

%% For wrapping figures in text
\usepackage{wrapfig}

@@

\title{Report On:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe}

@@

The low metallicity of early stars, specifically stars with high [$\alpha$/Fe] and low [Fe/H] values, indicate that their
nucleosynthesis occurred during a period after the first round of core-collapse supernovae but before large numbers of
Type Ia supernovae events. For decades scientists looked early stars in the halo of the Milky Way to study the early universe.
These Milky Way (MW) Halo stars have [Fe/H] values of $< -1.0$.

In the past decade efforts such as the Sloan Digital Sky Survey (SDSS) have uncovered a plethora of very dim dwarf spheroidal
(dSph) galaxies and ultra faint dwarfs. These dSph and ultra faint dwarfs have total luminosities in the range of
\(10^{5} L_{\odot} \lesssim L \lesssim 10^{7} L_{\odot}\) and \(L \lesssim 10^5 L_{\odot}\), respectively, which contain
stars with [Fe/H] values of $\sim -2.5$. With the use of medium resolution spectroscopy scientists recently uncovered a
moderate population of super low metal stars with [Fe/H] values $< -3.0$ within ultra fain dwarfs. Within the same systems
scientists did not find any stars with [Fe/H] $> -1.0$. In this population one galaxy, SEGUE-1, stood out from the rest. 
SEGUE-1's population of stars show increasing metallicity, in the form of $\alpha$-elements, but do not exhibit decreasing
[$\alpha$/Fe] ratios. 
This would indicate that the star formation phase in SEGUE-1 occurred before most, if not all, Type Ia supernovae events. This
also indicates that there was likely only one star formation phase within the galaxy.
\section{Novelty and Methods} \label{sec:novelty}

The authors of this paper made new spectrography measurements of six stars within SEGUE-1 using the Magellan/MIKE and Keck/HIRES
spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
stars that were chosen were the brightest stars in SEGUE-1 which allowed for high resolution spectrography. Using the spectrographs
the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, and neutron-capture elements.
The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
The detail for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
noise ratio (S/N) was only moderate with values between 20 and 50

\begin{table}[!h]
    \includegraphics[width=\textwidth]{obs_detail.png}
    \caption{Observing details for the six measured stars}
    \label{table:obs_detail}
\end{table}

\section{Results and Discussion} \label{sec:dicussion}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.85\textwidth]{spectra.png}
    \caption{Spectra of the six stars, in blue, bracketed by $CD -38^{\circ}245$ at the top and Arcturus at the bottom.
    the spectral lines of the elements are labeled at the bottom with the corresponding ranges of wavelengths.}
    \label{fig:spectra}
\end{figure}

@@

Using the spectrography data the authors also plotted abundance ratios [X/Fe] relative to the iron abundance [Fe/H] for the elements
that were measured. The dashed line at [X/Fe] = 0 indicates the ratio of the element in our Sun with positive values meaning higher
abundance and lower values indicating lower abundance, on a log scale. Notice that in all of the SEGUE-1 stars the abundance of
$\alpha$-elements such as Mg, Si, Ca, and Ti, are all above that of the Sun. Elements that are synthesized by other processes that
occur later in the timeline such as Al, Cr, and Mn, have consistent abundances lower than that of the Sun.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.6\textwidth]{elements.jpg}
    \caption{The abundance ratios [X/Fe] compared to the metallicity [Fe/H] of each of the elements that were measured with
    the spectroscopes. The six small red circles represent the SEGUE-1 stars measured in this article. The larger red circle
    is a SEGUE-1 star measured in a previous paper. The small black and blue circles represent MW halo stars measured from
    previous papers.}
    \label{fig:elements}
\end{figure}
\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.8\textwidth]{enrich.jpg}
    \caption{Enrichment Behavior plots for MW Halo stars, the six measured SEGUE-1 stars, a previously measured SEGUE-1 star,
    and stars from other classical dSph galaxies. These plots show the relationship between $\alpha$-element abundance (specifically
    Mg, Ca \& Ti) ratios [$\alpha$/Fe] and the metallicity [Fe/H] within the stars.}
    \label{fig:enrich}
\end{figure}

@@

\begin{wrapfigure}{r}{0.4\textwidth}
    \begin{center}
        \includegraphics[width=0.38\textwidth]{neutron_cap.jpg}
    \end{center}
    \caption{Birds}
    \label{fig:neutron_cap}
\end{wrapfigure}

@@

\section{Future Work} \label{sec:future}
